### 2023-05-24 application.tex
up

\begin{proof}
\alain{faire la preuve pour les VASS.} From \cite{DBLP:journals/corr/abs-2207-02697}...
\mathieu{En train de penser que la meilleure stratégie ici est de réduire "w.l.o.g" au cas où ils sont complémentaires encore faut-il montrer que ce serait without loss of generality.
}
When asking about resilience, in context, there are no true ``neutral'' configurations.
Hence from a VASS $V$, $\Safe$ and $\Bad$ semilinear, one can build VASS $V'$, $\Safe'$ semilinear, and $\Bad'$ complement of $\Safe'$ such that {\sc Resilience} holds for
$V$, $\Safe$ and $\Bad$ if and only if {\sc Resilience} holds for
$V'$, $\Safe'$ and $\Bad'$. For the construction, $V'$ will have two copies of the control states of $V$; $Q_{A}$ and $Q_{B}$, and will have two other VASS running in parallel checking whether or not the current configuration belong to $\Safe$ resp. $\Bad$. 
From a configuration with state in $Q_{A}$ you go to $Q_B$ when you are in a $\Bad$ place
and from a configuration with state in $Q_{B}$ you go to $Q_{A}$ when you are in a $\Safe$ place.
$\Safe'$ is $Q_A \times \N^d$ and $\Bad'$ is $Q_B \times N^d$.
\mathieu{...}
Without loss of generality hence let us consider only the case when $\Safe$ is semilinear
and $\Bad = S \setminus \Safe$ is semilinear too.
{\sc Resilience} asks whether $\Bad \subseteq \pred^*(\Safe)$.
We have $\post^*(\Bad) \setminus \Safe = \Bad$ by extension of $S \setminus \Safe = \Bad$.
Thus $\post^*(\Bad) = \Bad \cup (\Safe \cap \post^*(\Bad))$. Since $(\Safe \cap \post^*(\Bad)) \subseteq \pred^*(\Safe)$, we have
$$\post^*(\Bad) \subseteq \pred^*(\Safe) \quad iff \quad \Bad \subseteq \pred^*(\Safe).$$
Since it is decidable whether $\post^*(\Bad) \subseteq \pred^*(\Safe)$ when 
$\Bad$ and $\Safe$ are both semilinear \cite{DBLP:journals/corr/abs-2207-02697}, 
{\sc Resilience} is decidable.
\end{proof}

@@

We now consider the set 
% $\Bad \setminus (\pred^{\leq k}(q_{j_1}(\omega)) \cup \ldots \pred^{\leq k}(q_{j_\ell}(\omega)) )$.
$\Bad \setminus (\pred^{\leq k}(\uparrow q_{j_1}(\textbf{0})) \cup \ldots \cup \pred^{\leq k}(\uparrow q_{j_\ell}(\textbf{0})) )$.
% \mathieu{Is it actually possible to check whether or not it is finite ?}
% If it is finite then w
We inductively check for any element in the set whether or not it is possible to reach from it the set $\Safe$ in $k$ or less steps.
If the set is finite then we stop the procedure once we have checked found a witness that $k$-resilience does not hold or once we have checked for every element, whichever comes first.
If it is infinite then
$k$-resilience does not hold 
and we eventually find a witness that $k$-resilience does not hold.
Indeed, 
if
$\Bad \setminus (\pred^{\leq k}(\uparrow q_{j_1}(\textbf{0})) \cup \ldots \cup \pred^{\leq k}(\uparrow q_{j_\ell}(\textbf{0})) )$
is
infinite
then
there exists an element of the form $q(\textbf{u} )$
with $\textbf{u} > \textbf{v}_{\Bad} + (k+1) \cdot (c_{\max}, \ldots, c_{\max})$ 
that is in $\Bad$ but not in any of the $\pred^{\leq k}(\uparrow q_{j_i}(\textbf{0}))$,
and hence from which it is not possible at all to reach
$\Safe$ in $k$ or less steps. This also means that, even in the case where $\Bad \setminus (\pred^{\leq k}(\uparrow q_{j_1}(\textbf{0})) \cup \ldots \cup \pred^{\leq k}(\uparrow q_{j_\ell}(\textbf{0})) )$ is finite, we only need to check reachability of $\Safe$ in $k$ or less steps for the elements with vectorial component at most
$ \textbf{v}_{\Bad} + (k+1) \cdot (c_{\max}, \ldots, c_{\max})$. Binding the search space
thus lead to the $\EXPSPACE$ upper bound.
\end{proof}

@@

\begin{proposition}
{\sc Bounded-resilience } in VASS when $\Bad = \uparrow \Bad$ and $\Safe = S \setminus \Bad$ is decidable. \alain{quelle complexité ?}
\end{proposition}

>>>>

\begin{proof}
When asking about resilience, in context, there are no true ``neutral'' configurations.
Hence from a VASS $V$, $\Safe$ and $\Bad$ semilinear, one can build VASS $V'$, $\Safe'$ semilinear, and $\Bad'$ complement of $\Safe'$ such that {\sc Resilience} holds for
$V$, $\Safe$ and $\Bad$ if and only if {\sc Resilience} holds for
$V'$, $\Safe'$ and $\Bad'$. For the construction, $V'$ will have two copies of the control states of $V$; $Q_{A}$ and $Q_{B}$, and will have two other VASS running in parallel checking whether or not the current configuration belong to $\Safe$ resp. $\Bad$. 
From a configuration with state in $Q_{A}$ you go to $Q_B$ when you are in a $\Bad$ place
and from a configuration with state in $Q_{B}$ you go to $Q_{A}$ when you are in a $\Safe$ place.
$\Safe'$ is $Q_A \times \N^d$ and $\Bad'$ is $Q_B \times N^d$.

Without loss of generality hence let us consider only the case when $\Safe$ is semilinear
and $\Bad = S \setminus \Safe$ is semilinear too.
{\sc Resilience} asks whether $\Bad \subseteq \pred^*(\Safe)$.
We have $\post^*(\Bad) \setminus \Safe = \Bad$ by extension of $S \setminus \Safe = \Bad$.
Thus $\post^*(\Bad) = \Bad \cup (\Safe \cap \post^*(\Bad))$. Since $(\Safe \cap \post^*(\Bad)) \subseteq \pred^*(\Safe)$, we have
$$\post^*(\Bad) \subseteq \pred^*(\Safe) \quad iff \quad \Bad \subseteq \pred^*(\Safe).$$
Since it is decidable whether $\post^*(\Bad) \subseteq \pred^*(\Safe)$ when 
$\Bad$ and $\Safe$ are both semilinear \cite{DBLP:journals/corr/abs-2207-02697}, 
{\sc Resilience} is decidable.
\end{proof}

@@

We now consider the set 
% $\Bad \setminus (\pred^{\leq k}(q_{j_1}(\omega)) \cup \ldots \pred^{\leq k}(q_{j_\ell}(\omega)) )$.
$\Bad \setminus (\pred^{\leq k}(\uparrow q_{j_1}(\textbf{0})) \cup \ldots \cup \pred^{\leq k}(\uparrow q_{j_\ell}(\textbf{0})) )$.
% \mathieu{Is it actually possible to check whether or not it is finite ?}
% If it is finite then w
We inductively check for any element in the set whether or not it is possible to reach from it the set $\Safe$ in $k$ or less steps.
If the set is finite then we stop the procedure once we have checked found a witness that $k$-resilience does not hold or once we have checked for every element, whichever comes first.
If it is infinite then
$k$-resilience does not hold 
and we eventually find a witness that $k$-resilience does not hold.
Indeed, 
if
$\Bad \setminus (\pred^{\leq k}(\uparrow q_{j_1}(\textbf{0})) \cup \ldots \cup \pred^{\leq k}(\uparrow q_{j_\ell}(\textbf{0})) )$
is
infinite
then
there exists an element of the form $q(\textbf{u} )$
with $\textbf{u} > \textbf{v}_{\Bad} + (k+1) \cdot (c_{\max}, \ldots, c_{\max})$ 
that is in $\Bad$ but not in any of the $\pred^{\leq k}(\uparrow q_{j_i}(\textbf{0}))$,
and hence from which it is not possible at all to reach
$\Safe$ in $k$ or less steps. This also means that, even in the case where $\Bad \setminus (\pred^{\leq k}(\uparrow q_{j_1}(\textbf{0})) \cup \ldots \cup \pred^{\leq k}(\uparrow q_{j_\ell}(\textbf{0})) )$ is finite, we only need to check reachability of $\Safe$ in $k$ or less steps for the elements with vectorial component at most
$ \textbf{v}_{\Bad} + (k+1) \cdot (c_{\max}, \ldots, c_{\max})$. Binding the search space
thus leads to the $\EXPSPACE$ upper bound.
\end{proof}

@@

\begin{proposition}
{\sc Bounded-resilience } in VASS when $\Bad = \uparrow \Bad$ and $\Safe = S \setminus \Bad$ is in $\EXPSPACE$.
\end{proposition}
